Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/background.tex
removed a few repretitive sentences

\Ben[inline]{We need to discuss not only the background of BGP routing here, but 
also background about surveillance and censorship. We could probably shorten/tighten
the BGP stuff to make room.}

The interplay between the Internet and policy has a history as long as the
Internet itself, but in terms of national-scale interference with packets the
first prominent case of a state-sponsored system to achieve this is the
so-called ``Great Firewall of China,'' which was first documented in the
technical research literature in 2006 by Clayton \emph{et
al.}~\cite{Clayton:2006:IGF:2166520.2166523}.  As of 2017, 49 countries are
reported by the Freedom on the Net project~\cite{FOTN} to be ``partly free'' or
``not free''.  Large-scale Internet surveillance is also prominent and has a
long history, but surveillance is not as easy to measure as censorship so only
information dumps such as the 2013 Snowden revelations can give us a sense of
the prevalence and time periods related to surveillance.  National-scale
manipulation of packets for reasons other than censorship, for example to inject
malware or carry out distributed denial-of-service attacks, was first seen being
carried out by China's ``Great Cannon'' in 2015~\cite{badtraffic}.  More
recently Egypt was documented doing similar injections using a commercial
product~\cite{191996}.  This phenomena is more targeted and therefore more
stealthy than national-scale censorship, so may be more prevalent than just
these two countries.

>>>>

The interplay between the Internet and policy has a history as long as the
Internet itself, but in terms of national-scale interference with packets the
first prominent case of a state-sponsored system to achieve this is the
so-called ``Great Firewall of China,'' which was first documented in the
technical research literature in 2006 by Clayton \emph{et
al.}~\cite{Clayton:2006:IGF:2166520.2166523}. Large-scale Internet surveillance is also prominent and has a
long history, but surveillance is not as easy to measure as censorship so only
information dumps such as the 2013 Snowden revelations can give us a sense of
the prevalence and time periods related to surveillance.  National-scale
manipulation of packets for reasons other than censorship, for example to inject
malware or carry out distributed denial-of-service attacks, was first seen being
carried out by China's ``Great Cannon'' in 2015~\cite{badtraffic}.  More
recently Egypt was documented doing similar injections using a commercial
product~\cite{191996}.  This phenomena is more targeted and therefore more
stealthy than national-scale censorship, so may be more prevalent than just
these two countries.
